The \dealii Library, Version 9.0

### 2018-05-11 9.0/paper.tex
Added sentence about step-60

\marginpar{LH and others: Please add summaries of the new tutorial program.}
The \texttt{step-60} tutorial program shows \ldots

>>>>

The tutorial program \texttt{step-60} shows how to perform computations on
non-matching grids, and it presents advanced manipulation of
\texttt{ParameterHandler} objects, exploiting the new \texttt{ParameterAccessor}
and \texttt{ParameterAccessorProxy} classes. \texttt{step-60} solves a Poisson
problem on a domain $\Omega$, subject to equality constraints defined on an
embedded domain $\Gamma$. The embedded domain can be of co-dimension one or
co-dimension zero, and its definition is independent with respect to $\Omega$.
In order to enforce correctly the constraints, a non-matching coupling matrix
needs to be constructed. This is achieved using the new
\texttt{NonMatching::create\_coupling\_sparsity\_pattern} and
\texttt{NonMatching::create\_coupling\_mass\_matrix}, that exploit some new
functionality in the \texttt{GridTools} namespace.
